### 2018-08-08 article.tex
typo

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM EXAMPLES        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{example}[Gates counter]
  Let's start with a simple example, a gates counter homomorphism $N$ over the
    quantale the additive group of natural numbers.
  \begin{align*}
    N(f) & = 1 \\
    N(f \circ g) &= N(f) + N(g) \\
    N(f \otimes g) &= N(f) + N(g)
  \end{align*}
  On rewriting sequences we have
  \[
    N(f \Rightarrow g) = N(f) - N(g)
  \]
  Then the induced $\mathbb{Q}$-enriched category become a tool which give us
    the number of gates added or removed given a rewriting sequence.
\end{example}

\begin{example}[Depth \& time counters]
  Two similar counters can be made using the depth and the time of a circuit
  \begin{align*}
    D(f) &= 1 \\
    D(f \circ g) &= D(f) + D(g) \\
    D(f \otimes g) &= \max(D(f), D(g))
  \end{align*}
  and
  \begin{align*}
    T(f) &= t_f \\
    T(f \circ g) &= T(f) + T(g) \\
    T(f \otimes g) &= \max(T(f), T(g))
  \end{align*}
  With $t_f$ defined for the generators of the PROP.
  It is easily to check that
  \begin{align*}
    \max(D(f), D(g)) \preceq D(f) + D(g)
    \max(T(f), T(g)) \preceq T(f) + T(g)
  \end{align*}
  as required by the homomorphism.
\end{example}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%        HOMOMORPHISM EXAMPLES        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{example}[Gates count]
  Let's start with a simple example, a gates counter homomorphism $N$ over the
    quantale the additive group of natural numbers.
  \begin{align*}
    N(f) & = 1 \\
    N(f \circ g) &= N(f) + N(g) \\
    N(f \otimes g) &= N(f) + N(g)
  \end{align*}
  On rewriting sequences we have
  \[
    N(f \Rightarrow g) = N(f) - N(g)
  \]
  Then the induced $\mathbb{Q}$-enriched category become a tool which give us
    the number of gates added or removed given a rewriting sequence.
\end{example}

\begin{example}[Depth \& time count]
  Two similar counters can be made using the depth and the time of a circuit
  \begin{align*}
    D(f) &= 1 \\
    D(f \circ g) &= D(f) + D(g) \\
    D(f \otimes g) &= \max(D(f), D(g))
  \end{align*}
  and
  \begin{align*}
    T(f) &= t_f \\
    T(f \circ g) &= T(f) + T(g) \\
    T(f \otimes g) &= \max(T(f), T(g))
  \end{align*}
  With $t_f$ defined for the generators of the PROP.
  It is easily to check that
  \begin{align*}
    \max(D(f), D(g)) \preceq D(f) + D(g) \\
    \max(T(f), T(g)) \preceq T(f) + T(g)
  \end{align*}
  as required by the homomorphism.
\end{example}
